### 2012-03-29 contents.tex
Changing bugzilla workflow figure to a more compact one.

However, mining bug repositories has its own risks. Previous research has identified problems of missing data (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Aranda2009}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

\begin{figure}[ht]
	\centering
		\includegraphics[scale=0.4]{bugzilla.png}
	\caption{Workflow for Bugzilla. Source: \url{http://www.bugzilla.org/docs/2.18/html/lifecycle.html}.}
	\label{fig:bugzilla}
\end{figure}

@@

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r|c}
			% \toprule
			\textbf{\centering Project} & 
			\MyHead{1.2cm}{\textbf{\centering QA team size}} & 
			\MyHead{1.6cm}{\textbf{\% of verifications by QA team}} &
			\MyHead{2.7cm}{\textbf{Distribution of ratio (bugs verified / bugs fixed) per developer}} \\
			\hline
			\textbf{Eclipse} & & & 
			   \multirow{6}{*}{\includegraphics[scale=1]{ratio}}\\
			\quad Platform        & 4 (2.4\%)  &  1.1\% &  \\
			\quad EMF             & 0 (0.0\%)  &  0.0\% & \\
			\textbf{NetBeans} & & \\
			\quad Platform       & 25 (18.8\%) & 80.1\% & \\
			\quad V.Control & 5 (20.8\%) & 93.2\% & \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	No references to formal verification were found. Regarding static analysis, only 4 references were found; upon inspection, it was found that only one reference (bug report #15242 for NetBeans/Platform) implies the use of a static analysis tool in the verification process.

>>>>

However, mining bug repositories has its own risks. Previous research has identified problems of missing data \cite{Arand2009} (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Antoniol2008}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

\begin{figure}[ht]
	\centering
		\includegraphics[width=0.48\textwidth]{bugzilla}
	\caption{Simplified workflow for Bugzilla. Adapted from \url{http://www.bugzilla.org/docs/2.18/html/lifecycle.html}.}
	\label{fig:bugzilla}
\end{figure}

@@

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r|c}
			% \toprule
			\textbf{\centering Project} & 
			\MyHead{1.2cm}{\textbf{\centering QA team size}} & 
			\MyHead{1.6cm}{\textbf{\% of verifications by QA team}} &
			\MyHead{2.7cm}{\textbf{Distribution of ratio (bugs verified / bugs fixed) per developer}\vspace{2mm}} \\
			\hline
			\textbf{Eclipse} & & & 
			   \multirow{6}{*}{\includegraphics[scale=1]{ratio}}\\
			\quad Platform        & 4 (2.4\%)  &  1.1\% &  \\
			\quad EMF             & 0 (0.0\%)  &  0.0\% & \\
			\textbf{NetBeans} & & \\
			\quad Platform       & 25 (18.8\%) & 80.1\% & \\
			\quad V.Control & 5 (20.8\%) & 93.2\% & \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	No references to formal verification were found. Regarding static analysis, only 4 references were found; upon inspection, it was found that only one reference (bug report 15242 for NetBeans/Platform) implies the use of a static analysis tool in the verification process.
